Hypertension and microbiome

### 2019-01-23 articletwo.Rmd
Minor

@@

>>>>

# Sources

### Officer functions

```{r Officer importer, code=readLines("articleone-officer.R")}
source("articletwo-officer.R")
```

@@

## Characteristics of the study sample. (Table 1.)

```{r Characteristics}
tbl1 <- xtableformatter(characteristics(dset$fr02$data.full)) %>%
    flextable::width(j = 1, width = 3) %>%
    flextable::width(j = 2, width = 1.2) 
```

```{r Write characteristics}
tbl1head <- "Characteristics of the study sample."
tbl1foot <- "Continuous variables are presented as mean (standard deviation). Categorical variables reported as absolute and relative frequencies. BMI indicates body mass index."
writetable(doc, tbl1, number = 1, tbl1head, tbl1foot)
```
